FireSim2019_ManuscriptFigures

### 2023-03-16 Manuscript-figures.Rmd
Updating scripts used in manuscript

# Metadata
```{r, include=FALSE}
df.meta <- read.csv('../data/all-sample-metadata.csv')

@@

# Starting phyloseq:
### Normalized + tree
ps.norm.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)

@@

ps.raw.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')

@@

# Figure 2 (burn temperature, pH and C:N change, respiration coefficients):
```{r}
# Temperatures ----
df.Temp <-read.csv('../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))

pTemp = ggplot(df.Temp, aes(x = time_hr, 
                          y = Temp)) + 
  geom_point(aes(color = Thermo_position), size=1) +
  theme_bw()+
  facet_grid(burn.trtmt~Thermo_position,scales = 'free_y', 
             labeller = labeller(Thermo_position = ThermoLabels,
                                 burn.trtmt = BurnLabels)) +
  labs(x = "Time (h)",
       y = expression(paste("Temperature ( ",degree ~ C, ")")),
       color = "Soil depth") + 
  scale_color_manual(values = c('black','grey40'),
                     labels = c('O horizon/mineral \n interface','9 cm'),
                     breaks = c('Mid','Low')) + 
  theme(axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size=16),
        strip.text.y = element_text(size=16), 
        strip.text.x = element_text(size=16), 
        legend.text = element_text(size=16),
        legend.title = element_text(size=16), 
        legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92")) 
pTemp

# pH and C:N change ----
pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = pH, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil pH',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

pChange_CN  <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = C.N.ratio, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil C:N',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

# Respiration coefficients ----
df.coefs <- subset(df.meta, incub.trtmt == 'LIwA' &
                     horizon == 'O' & texture != 'organic')

@@

pResp2 = ggplot(subset(df.stack, coefs %in% c('M1','M2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Fractional pool size',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=25, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

pResp1 = ggplot(subset(df.stack, coefs %in% c('k1','k2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Decay rate',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

cowplot::plot_grid(pResp2, pResp1, ncol=1)

@@

# Figure 3: RNA and DNA concentration (ng/g soil)
```{r}
df <- read.csv('../data/raw-data/pb-RNA-and-DNA-conc.csv')

@@

p1 = ggplot(df) + 
  geom_boxplot(aes(x=burn.trtmt, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = horizon),alpha = 0.7, varwidth = FALSE) + 
  theme_bw()+
  facet_wrap(~DNA.type, ncol=2, labeller = labeller(DNA.type = NaLabels))+
  labs(x= 'Burn treatment',
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Concentration (ug/g soil)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                    limits = c('O','A'),
                    labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                   labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 13),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'right',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
p1

test <- aov(nucleic.acid.conc.in.soil.ng.per.g ~ burn.trtmt, data = subset(df, DNA.type == 'cDNA' & horizon == 'O' & burn.trtmt != 'wet'))
summary(test)
TukeyHSD(test)

@@

# Plots ----
p=ggplot(subset(df.distances, DNA.type == 'cDNA')) + 
  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.burned.and.control, fill = horizon),
               alpha = 0.7) +
  theme_bw() +
  facet_wrap(~incub.trtmt, ncol=4,
             labeller = labeller(incub.trtmt = IncubLabels)) + 
  labs(x='Burn treatment',
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('wet','dry'),
                   labels = c('Wet soil \nburn','Dry soil \nburn')) +
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=18),
        legend.title = element_text(size=18),
        legend.text = element_text(size=18),
        strip.text = element_text(size=18)) + 
  ylim(0,1)

@@

# Figure 4 - weighted mean gene copy number
Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
```{r}
df.WMCN.pb <- read.csv('../data/WtMeanCopyNum_pb_gDNA.csv')
df.WMCN.SI <- read.csv('../data/WtMeanCopyNum_SI.csv')
df.WMCN.LIwA <- read.csv('../data/WtMeanCopyNum_LIwA.csv')

@@

p1 = ggplot(data = subset(df.WMCN, incub.trtmt != 'LIwA')) + 
  geom_boxplot(aes(x=burn.trtmt, y=WtMeanCopyNum, fill=horizon),alpha=0.7)+
  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels))+
  theme_bw() + 
  scale_fill_manual(values = c('black','grey50'),
                     labels = c('Organic','Mineral'),
                     limits = c('O','A'))+
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  labs(x='Burn treatment',
       y='Weighted mean predicted \n16S rRNA gene copy number',
       fill = 'Soil horizon') +
  theme(axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        strip.text = element_text(size=14),
        legend.position = 'right',
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10))) +
  ylim(1,NA)

@@

# Compare copy number of positive/negative responders: ----
df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
RDP <- read.csv('../data/All-OTUs-CopyNum.csv')

df.fast <- subset(df.full, experiment == 'fast growth' &
                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
  mutate(fast.est = Estimate)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.Estimate = max(Estimate)) %>%
  subset(Estimate == max.Estimate) %>%
  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
                    Species, DNA.type, fast.est)) %>%
  unique()

@@

# Figure 5 - Calculate bray-curtis dissimilarity for autoclaving
```{r, message = FALSE}
df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')

@@

# plot: Dry soil burns
p3=ggplot(subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry'),
         aes(x=change.pH, y = BC.distance.btw.burned.and.control, color = horizon, shape = horizon)) + 
  geom_point(size=3, alpha = 0.8) +
  theme_bw() +
  facet_wrap(~horizon,ncol=2,
             labeller = labeller(horizon = HorizonLabels),
             scales = 'fixed') + 
  labs(x = expression(Delta~'pH with burning'),
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       color = 'Soil horizon',
       shape = 'Soil horizon') + 
  scale_color_manual(values = c('black', 'grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title.x = element_text(size=14, margin = margin(t=10)),
        axis.title.y = element_text(size=14, margin = margin(r=10)),
        axis.text = element_text(size=12),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        strip.text = element_text(size=14),
        panel.spacing.x = unit(2, "lines"),
       legend.position = 'right') +
  stat_smooth(data = subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry' & horizon == 'O'),
              method=lm,se = FALSE,color='black') +
    ylim(0,1)

@@

>>>>

# Metadata
```{r, include=FALSE}
df.meta <- read.csv('../../data/all-sample-metadata.csv')

@@

# Starting phyloseq:
### Normalized + tree
ps.norm.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)

@@

ps.raw.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')

@@

# Figure 2 (burn temperature, pH and C:N change, respiration coefficients):
```{r}
# Temperatures ----
df.Temp <-read.csv('../../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))

pTemp = ggplot(df.Temp, aes(x = time_hr, 
                          y = Temp)) + 
  geom_point(aes(color = burn.trtmt), size=1) +
  theme_bw()+
  facet_wrap(~Thermo_position,scales = 'free_y', ncol=1,
             labeller = labeller(Thermo_position = ThermoLabels,
                                 burn.trtmt = BurnLabels)) +
  labs(x = "Time (h)",
       y = expression(paste("Thermocouple temperature ( ",degree ~ C, ")")),
       color = "Burn treatment") + 
  #scale_color_manual(values = c("black","grey70"),
   #                  labels = c('O horizon/mineral \n interface','9 cm'),
    #                 breaks = c('wet','dry')) + 
  scale_color_manual(values = c('orange','red'),
                     limits = c('wet','dry'),
                     labels = c('Moist soil burn','Dry soil burn')) +
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size=14),
        strip.text.y = element_text(size=14), 
        strip.text.x = element_text(size=14), 
        legend.text = element_text(size=12),
        legend.title = element_text(size=12), 
        legend.position = 'right',
       strip.background = element_rect(colour="black", fill="grey92")) +
  geom_hline(yintercept=100)
pTemp

# pH and C:N change ----
pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=horizon, y = pH, fill = burn.trtmt), varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Soil horizon',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil pH',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
  # scale_fill_manual(values = c("slateblue4","palegreen3"),
  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
  #                    limits = c('O','A'),
  #                    labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

pChange_CN  <- ggplot(subset(df.meta, incub.trtmt == 'SI' &site !=10)) + 
  geom_boxplot(aes(x=horizon, y = C.N.ratio, fill = burn.trtmt), varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Soil horizon',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil C:N',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
  # scale_fill_manual(values = c("slateblue4","palegreen3"),
  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
  #                    limits = c('O','A'),
  #                    labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=12),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=12),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

@@

# Stats ----
df.stats <- subset(df.meta, incub.trtmt == 'SI' )

test = aov(C.N.ratio ~ burn.trtmt*horizon, subset(df.stats))
summary(test)
TukeyHSD(test)

# Respiration coefficients ----
#   Decay model coefficients at end of 5 week incubation (Days=34)
#   after adjusting for total C
df.coefs <- read.csv('../../data/2-pool-decay-model-output-SI-adjusted-for-total-C.csv') %>%
  subset(t==34) 
# df.coefs <- read.csv('../../data/2-pool-decay-model-output-LIwA-adjusted-for-total-C.csv') %>%
#   subset(t==180)

@@

pResp2 = ggplot(subset(df.stack, coefs %in% c('M1','M2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value, fill=burn.trtmt),varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Fractional pool size',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet burn','dry burn'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('control','wet burn','dry burn'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 12),
        legend.title = element_text(size=12),
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=25, l=10)),
        strip.text = element_text(size=12),
        legend.text = element_text(size=12),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

pResp1 = ggplot(subset(df.stack, coefs %in% c('k1','k2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value, fill=burn.trtmt),varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Decay rate',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet burn','dry burn'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('control','wet burn','dry burn'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 12),
        legend.title = element_text(size=12),
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=12),
        legend.text = element_text(size=14),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

cowplot::plot_grid(pResp2, pResp1, ncol=2)

@@

# Figure 3: RNA and DNA concentration (ng/g soil)
```{r}
df <- read.csv('../../data/raw-data/pb-RNA-and-DNA-conc.csv')

@@

p1 = ggplot(df) + 
  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
  theme_bw()+
  facet_wrap(~DNA.type, ncol=2, labeller = labeller(DNA.type = NaLabels))+
  labs(x= 'Soil horizon',
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Concentration\n(ug/g soil)',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  # scale_fill_manual(values = c("darkgreen","grey70"),
  #                   limits = c('O','A'),
  #                   labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 13),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
p1

p_DNA = ggplot(subset(df, DNA.type == 'gDNA')) + 
  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
  theme_bw()+
  labs(x= 'Soil horizon',
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'DNA concentration\n(ug/g soil)',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  # scale_fill_manual(values = c("darkgreen","grey70"),
  #                   limits = c('O','A'),
  #                   labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 13),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

p_RNA = ggplot(subset(df, DNA.type == 'cDNA')) + 
  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
  theme_bw()+
  labs(x= 'Soil horizon',
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'RNA concentration\n(ug/g soil)',
       fill = 'Burn treatment') + 
  scale_fill_manual(values = c('grey50','orange','red'),
                     limits = c('control','wet','dry'),
                     labels = c('Unburned control','Moist soil burn','Dry soil burn')) +
  scale_x_discrete(limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  # scale_fill_manual(values = c("darkgreen","grey70"),
  #                   limits = c('O','A'),
  #                   labels = c('Organic','Mineral')) +
  # scale_x_discrete(limits = c('control','wet','dry'),
  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 13),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

cowplot::plot_grid(p_DNA, p_RNA, ncol=2)

test <- aov(nucleic.acid.conc.in.soil.ng.per.g ~ burn.trtmt*horizon, data = subset(df, DNA.type == 'gDNA'))
summary(test)
TukeyHSD(test)

@@

# Plots ----
p=ggplot(subset(df.distances, DNA.type == 'cDNA')) + 
  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.burned.and.control, fill = horizon),
               alpha = 0.7) +
  theme_bw() +
  facet_wrap(~incub.trtmt, ncol=4,
             labeller = labeller(incub.trtmt = IncubLabels)) + 
  labs(x='Burn treatment',
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('wet','dry'),
                   labels = c('Moist soil \nburn','Dry soil \nburn')) +
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=18),
        legend.title = element_text(size=18),
        legend.text = element_text(size=18),
        strip.text = element_text(size=18)) + 
  ylim(0,1)

@@

# Figure 4 - weighted mean gene copy number
Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
```{r}
df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')

@@

p1 = ggplot(data = subset(df.WMCN, incub.trtmt != 'LIwA')) + 
  geom_boxplot(aes(x=burn.trtmt, y=WtMeanCopyNum, fill=horizon),alpha=0.7)+
  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels))+
  theme_bw() + 
  scale_fill_manual(values = c("darkgreen","grey70"),
                     labels = c('Organic','Mineral'),
                     limits = c('O','A'))+
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
  labs(x='Burn treatment',
       y='Weighted mean predicted \n16S rRNA gene copy number',
       fill = 'Soil horizon') +
  theme(axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        strip.text = element_text(size=14),
        legend.position = 'right',
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10))) +
  ylim(1,NA)

@@

# Compare copy number of positive/negative responders: ----
df.full.OTU <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
RDP <- read.csv('../../data/All-OTUs-CopyNum.csv')

df.fast <- subset(df.full.OTU, experiment == 'fast growth' &
                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
  mutate(fast.est = Estimate)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.Estimate = max(Estimate)) %>%
  subset(Estimate == max.Estimate) %>%
  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
                    Species, DNA.type, fast.est)) %>%
  unique()

@@

# Figure 5 - Calculate bray-curtis dissimilarity for autoclaving
```{r, message = FALSE}
df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')

@@

# plot: Dry soil burns
p3=ggplot(subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry'),
         aes(x=change.pH, y = BC.distance.btw.burned.and.control, color = horizon, shape = horizon)) + 
  geom_point(size=3, alpha = 0.8) +
  theme_bw() +
  facet_wrap(~horizon,ncol=2,
             labeller = labeller(horizon = HorizonLabels),
             scales = 'fixed') + 
  labs(x = expression(Delta~'pH with burning'),
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       color = 'Soil horizon',
       shape = 'Soil horizon') + 
  scale_color_manual(values = c("darkgreen","grey70"),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title.x = element_text(size=14, margin = margin(t=10)),
        axis.title.y = element_text(size=14, margin = margin(r=10)),
        axis.text = element_text(size=12),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        strip.text = element_text(size=14),
        panel.spacing.x = unit(2, "lines"),
       legend.position = 'right') +
  stat_smooth(data = subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry' & horizon == 'O'),
              method=lm,se = FALSE,color='black') +
    ylim(0,1)

@@

# Responders as fraction of total reads
```{r}
df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')

ps.responders <- prune_taxa(taxa_names(ps.norm.full) %in% df$OTU, ps.norm.full)

df.melt <- psmelt(ps.responders)

responders <- df.melt %>% group_by(Sample) %>% summarize(Abundance) 
max(responders$Abundance)
mean(responders$Abundance)

dry <- subset(df.melt, burn.trtmt == 'dry') %>% subset(select = c(Sample, horizon, burn.trtmt, Abundance, incub.trtmt, Thermo.mid.max)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))

summary(dry)

# Total gDNA reads in lab experiments: 39115
# Total reads in lab experiments: 43450
# Number responders = 117
# max abundance in lab data = 60%
# mean abundance, dry burns = 0.15% +/- 14%

df.frac.of.total <- df.melt %>% subset(select = c(Sample, horizon, burn.trtmt, Veg.type, Abundance, DNA.type, incub.trtmt, Thermo.mid.max, site)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
